%----------------------------------------------------------------------
\chapter*{Introduction}\label{ch:introduction}
\addcontentsline{toc}{chapter}{Introduction}
%----------------------------------------------------------------------

This document provides instructions for laboratory work in the field of embedded systems. The laboratory is part of the Data Handling course of the UPM Máster Universitario de Sistemas Espaciales (MUSE) program.
The laboratory is based on a computer kit that is used to build a simplified version of a satellite on-board software system (OBSW). An instance of the laboratory kit will be made available to every student registered in the course during the laboratory session.

Students are required to use their own personal computer, running Windows, MacOS, or GNU/Linux, to carry out the laboratory assignments. 
The outline of the laboratory assignments to be carried out is as follows:
\begin{enumerate}
\item	Installation of a native programming environment.
\item	Installation of the cross-platform programming tools.
\item   Simple housekeeping program.
\item   Tasking program.
\item   Distributed program.
\item   Real-time program, including temporal analysis
\item	Real-time program with Attitude Control System.
\item   On-board data handling (OBDH) system.
\end{enumerate}

%----------------------------------------------------------------------
\section*{References}
\addcontentsline{toc}{section}{References}

The following documents contain additional information about the software
and hardware tools used to develop the work:

\subsection*{Hardware}
\begin{enumerate}
\item	\href{https://www.st.com/resource/en/data\_brief/stm32f4discovery.pdf}{STMicroelectronics. DB1421 Data Brief.  STM32F4DISCOVERY - Discovery kit with STM32F407VG MCU.}
\item \href{https://www.st.com/content/ccc/resource/technical/document/user\_manual/70/fe/4a/3f/e7/e1/4f/7d/DM00039084.pdf/files/DM00039084.pdf/jcr:content/translations/en.DM00039084.pdf}{STMicroelectronics. UM1472 User manual - Discovery kit with STM32F407VG MCU.}
\item \href{https://www.st.com/resource/en/datasheet/dm00037051.pdf}{STMicroelectronics. DS 8626. Data sheet - STM32F405xx, STM32F407xx. ARM Cortex-M4 32b MCU+FPU, 210DMIPS, up to 1MB Flash/192+4KB RAM, USB OTG HS/FS, Ethernet, 17 TIMs, 3 ADCs, 15 comm. interfaces \& camera.}
\item \href{https://www.st.com/content/ccc/resource/technical/document/reference\_manual/3d/6d/5a/66/b4/99/40/d4/DM00031020.pdf/files/DM00031020.pdf/jcr:content/translations/en.DM00031020.pdf}{STMicroelectronics. RM0090 Reference manual - STM32F405/415, STM32F407/417, STM32F427/437 and STM32F429/439 advanced Arm\copyright-based 32-bit MCUs.}
\end{enumerate}

\subsection*{Software}

The following manuals are available from the ``Help" menu in the GNAT Programming Studio (GPS):
\begin{enumerate}
\item \href{http://www.ada-auth.org/standards/rm12i\_w\_tc1/html/RM-TTL.html}{Ada Reference Manual.}
\item	GPS User's Guide.
\item	GNAT User's Guide for Native Platforms.
\item	GNAT User's Guide Supplement for Cross Platforms
\item	GNAT Reference Manual.
\end{enumerate}

%----------------------------------------------------------------------

\section*{Acronyms}
\addcontentsline{toc}{section}{Acronyms}

\begin{entry}{RAVENSCAR}
\item[ADC] Analog to Digital Converter.
\item[DAC] Digital to Analog Converter.
\item[FPU] Floating Point Unit.
\item[GCC] GNU compilation system..
\item[GDB] GNU Debugger.
\item[GNAT] GNU Ada TranslatorDebugger.
\item[GNU] GNU is not Unix.
\item[GPL] GNU Public License.
\item[GPS] GNAT Programming Studio.
\item[LGPL] Lesser GNU Public License (formerly Library GPL).
\item[MCU] Microcontroller Unit.
\item[OBC] On-Board Computer.
\item[OBDH] On-Board Data Handling.
\item[OBSW] On-Board Software.
\item[OS] Operating System.
\item[PC] IBM Personal Computer architecture.
\item[TC] Telecommand.
\item[TM] Telemetry.
\item[USART] Universal Synchronous Asynchronous Receiver Transmitter.
\item[USB] Universal Serial Bus.
\end{entry}

