%!TEX root = practica.tex
%===============================================================================
\chapter{Temperature sensor}\label{ap:sensor}
%\addcontentsline{toc}{chapter}{Temperature sensor}
%----------------------------------------------------------------------

The STM32F407 reference manual (section 13.10) states that the internal temperature sensor of the MCU is internally cabled to the ADC1\_IN16 analog input channel. The steps required to read the sensor are:

\begin{enumerate}
	\item Select ADC1\_IN16 input channel in the ADC.
	\item Select a sampling time greater than the minimum sampling time specified in the datasheet (see table~\ref{tb:sensor} below).
	\item Set the TSVREFE bit in the ADC\_CCR register to wake up the temperature sensor from power down mode.
	\item Start the ADC conversion by setting the SWSTART bit (or by external trigger).
	\item Read the resulting VSENSE data in the ADC data register.
	\item Calculate the temperature using the following formula:
	
	Temperature (in \degree{C}) = {(VSENSE - V25) / Avg\_Slope} + 25
	
	Where:
	\begin{itemize}
		\item V25 = VSENSE value for 25 \degree{C} (table~\ref{tb:sensor})
		\item Avg\_Slope = average slope of the temperature vs. VSENSE curve (table~\ref{tb:sensor}).
	\end{itemize}
\end{enumerate}

The sensor has a startup time after waking from power down mode before it can output VSENSE at the correct level. The ADC also has a startup time after power-on, so to minimize the delay, the ADON and TSVREFE bits should be set at the same time.

The sensor has a range of -40 to 125 \degree{C}, with a precision of $\pm$1.5 \degree{C}. Its main characteristics are described in the STM32F407 datasheet (table~\ref{tb:sensor}).

\begin{table}[htb]
	\begin{center}
		\begin{tabular}{llllll} \hline
			Symbol & Parameter & Min & Typ & Max & Unit \\ \hline
			TL & VSENSE linearity with temperature & - & $\pm1$ & $\pm2$ & \degree{C}\\
			Avg\_Slope & Average slope & - & 2.5 & & mV/\degree{C}\\
			V25 & Voltage at 25 \degree{C} & - & 0.76 & & V\\
			tSTART & Startup time & - & 6 & 10 & $\mu{s}$\\
			TS\_temp & ADC sampling time when reading & 10 & - & - & $\mu{s}$\\
			& the temperature (1 \degree{C} accuracy) &  &  &  & \\ \hline
		\end{tabular}
		\caption{STM32F407 temperature sensor characteristic.}
		\label{tb:sensor}
	\end{center}
\end{table}

The Ada Drivers Library includes the package STM32.ADC, which provides facilities for handling the analog to digital converter.
